\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2025-02-23 Manuscript/reply2.tex
smoothed responses

We sincerely thank the Editor and Associate Editor for tentatively accepting our
submission and are proud to present our most recent revisions.

The manuscript has been revised accordingly with the following most
notable changes:
\begin{enumerate}
\item
  The focus of the study has been clarified in the completely
  rewritten introduction. The two objectives are 1) to investigate
  whether the reaction times at the 2022 World Championships were
  significantly different from the other competitions; and 2) to
  assess the appropriateness of the 0.1-second threshold.
\item
  Additional data

Point-by-point responses to the comments are as follows, with the
comments quoted in \emph{\color{darkblue} italic and blue}.
\end{enumerate}

@@

We thank the reviewer for the accurate summary of our contributions

@@

@@

Thank you for this suggestion, we have decided to re-organize our paper as a
result. Now, the first half of the paper is dedicated to the analysis of
athletes competing faster in 2022 and the second half is dedicated to the
analysis of the reaction time barrier, with an introduction and discussion to
show the connectivity of these problems.

@@

@@

@@

>>>>

We sincerely thank the Editor for tentatively accepting our submission
and Reviewer~1 for the additional suggestions. We are pleased to
present our final revisions.

The manuscript has been revised as follows, with the most notable
changes being:
\begin{enumerate}
\item
  Restructuring: The manuscript is now organized into four
  sections: Introduction, Analysis of 2022 Times, Analysis of a Proper
  RT Barrier, and Discussion. The second and third sections
  further include subsections for Data, Methods, and Results to
  enhance clarity and readability.
\item
  General Refinements: The manuscript has been carefully revised to
  improve clarity, coherence, and overall presentation.
\end{enumerate}

Point-by-point responses to the comments are as follows, with the
original comments quoted in \emph{\color{darkblue} italic blue}.

@@

Thank you for the thoughtful feedback and for recognizing the
improvements in our revision. The remaining points are well taken, and
we address them below.

@@

Distinguishing between the datasets used in each section was a valid
concern. To improve clarity, the paper has been restructured so that
each problem’s data, methods, and results appear consecutively, making
it easier to follow. The dataset for the 2022 analysis is now
described in the second paragraph of Section~2.1.1, while the dataset
for the RT barrier analysis is introduced in the first paragraph of
Section~3.1.

@@

This was an excellent suggestion, and we appreciate the insight. To
improve clarity and better align the results with the research
questions, the paper has been reorganized. Section~2 now focuses
on whether athletes competed faster in 2022, while Section~3
examines the RT barrier. The Introduction and Discussion
sections provide context and highlight the connection between these
two analyses.

@@

The manuscript has been further refined for clarity and
consistency. The language in Table~1 is now uniform. With the
restructuring, the definitions of the symbols in Table~2 are now
included within the same section, making them easier to connect.

@@

\jy{Admit the limitation of the study in the discussion and point to
  the location of the addition.}

We have added additional explanations in the discussion section to address both
seasonality and age, although we don't think either one will be largely
impactful.  By including times from athletes in both 2019 and 2022, there are
athletes who got older from 2019 to 2022 but athletes in 2022 will be younger
than they were in 2023.  Including both comparisons is meaningful as it helps
diminish this effect.  Likewise while seasonality may impact the 2022 national
level comparison, the 2019 and 2023 comparisons mitigate this factor.

@@

We appreciate the thoughtful feedback and are glad the technical work
is recognized as solid. The revisions have focused on improving the
organization and clarity of the paper to better communicate the key
findings.
